Investigate bsa differences

### 2022-02-02 Rmd/Investigate bsa diferences.Rmd
Investigate bsa difference between raw data and du bois formula

---
title: "Flatiron cleaning"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

@@

@@

```{r loadd}
loadd(drugs)
creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
```

# `r emo::ji("spiral_notepad")` This report is using **adjusted weight**

# `r emo::ji("spiral_notepad")` Reminders of each capping and formula:

Creatinine data are capped as :  
- creat < 0.7 was set at 0.7  
- creat > 3 are eliminated

ideal_weight is calculated :
- height <= 1.524               ~ 45.5 + 2.3,
- height > 1.524                ~ 45.5 + (2.3 * (((`height` - 1.524) / 0.0254)))

adjusted_weight :
- ((`weight` - `ideal_weight`) * 0.40) + `ideal_weight`

actual_bmi = weight / (height * height)

CrCl calculation :

IF actual_bmi >= 25 :
$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
IF actual_bmi < 25 :

$$adjusted\_CrCl = \frac{(140 - ageatdx) * adjusted\_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
In both cases CrCl is capped at 125.  
<br>

Calculating more BSA values :
$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
<br>

I clean the data up by keeping the `relativeorderedamount`:  
- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
- >= 2  & <= 6   for platin and with a unit in `AUC`

<br>

<!-- mutate(adjusted_expected_dose = case_when( -->
<!--     drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25), -->
<!--     drugname == "paclitaxel"                  ~ BSA * target_auc  -->
<!--     # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug -->
<!--   )) %>%  -->
<!--   mutate(adjusted_expected_dose = case_when( -->
<!--     adjusted_expected_dose > 900 & -->
<!--       target_auc == 6              ~ 900, -->
<!--     adjusted_expected_dose > 750 & -->
<!--       target_auc == 5              ~ 750, -->
<!--     TRUE                           ~ adjusted_expected_dose -->
<!--   )) -->

`adjusted_expected_dose` is:  
-`target_auc` * (`adjusted CrCl` + 25)   -> for `drugname` == "carboplatin"  
-`BSA` * `target_auc`                    -> for `drugname` == "paclitaxel"
(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).

<br>

<!-- relative_dose_intensity = amount / adjusted_expected_dose -->

Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ received}{adjusted\ expected\ dose}$$

<br>

<span style="color:red">**Please confirm everything is correct**</span>

# I. Drug episode cleaning

- Select episodedatasource == "Administrations"

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```
But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.

- Combine multiple administrations of the same drug at the same date
Flatiron says:
There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.  
For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.  
Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.   
Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
```{r combine amount same drug one day}
combined_drugs <- drugs %>% 
  # Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate,
           drugname, units, ismaintenancetherapy) %>%
  summarise_at(vars(route, amount), paste, collapse = ";") %>% # keep them in the data then do sum
  mutate(route = case_when(
    str_detect(route, ";")            ~ "Intravenous", # I checked that all the combined administration are IV
    TRUE                              ~ route
  )) %>% 
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  ungroup() %>% 
  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
  purrr::keep(~!all(is.na(.))) %>%
  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 so remove
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  ))# %>%

@@

- Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
```{r line coding}
therapy_line <- combined_drugs %>% 
  # bind again with clinical - was lost while summarizing
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  # Define Adjuvant, Neoadjuvant, chemo or surgery
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = 
           factor(chemotherapy_type, levels = 
                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_neo, had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>%

@@

  # 6.Add a 30 day rule to switch linenumber----
  # group_by(patientid, linenumber_new) %>% 
  # arrange(episodedate) %>% 
  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
  # ungroup() %>% 
  # group_by(patientid) %>% 
  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37

@@

  # Look at dose dense
  # Code how many time a drug comes up in a cycle
  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
  mutate(dose_dense = n()) %>% 
  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
  ungroup()

  # # CODE FOR SKIPPED CYCLE
  # group_by(patientid, linenumber_new) %>% 
  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
  # 
  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
  # mutate(n = row_number(drugname)) %>%
  # 
  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
  # fill(base_days_between_cycle, .direction = "downup") %>% 
  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
  # group_by(patientid, linenumber_new) %>%
  # mutate(drug_count_perline = n()) %>%
  # mutate(skipped_cycle_indays1 = ifelse(
  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
  # group_by(patientid) %>% 
  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
  # ungroup()

# rm(drugs, drugs1, therapy_line)
therapy_cycle %>% distinct(patientid) %>% nrow()
```

<br>

- Bind everything together to calculate target auc/target dose and expected dose

(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organization - You can find the calculations formula at the end of the document)  
When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`. It can be days in between but it can also be more.

`r emo::ji("check")`  
We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line

@@

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_bsa < 31 &
           bsa_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_bsa < 31 &
             # bsa_date < lineenddate &
             bsa_date > surgerydate)
      )                                          ~ interval_bsa,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    (therapy == "Upfront Surgery" &
       interval_auc < 31 &
       # auc_date < lineenddate &
       auc_date > surgerydate)                  ~ interval_auc,

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_auc < 31 &
           auc_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_auc < 31 &
             # auc_date < lineenddate &
             auc_date > surgerydate)
      )                                          ~ interval_auc,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)

Treatment1 %>% distinct(patientid) %>% nrow()
```

```{r plot interval}
# Treatment %>% 
#   ggplot(aes(x= interval_creat)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# # Treatment %>% 
# #   ggplot(aes(x= interval_height)) +
# #   geom_bar() +
# #   coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_weight)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_bsa)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_auc)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
```

<!-- # Variable for filtering -->

```{r rule between diagnosis and treatment}
Treatment <- Treatment1 %>% 
  filter(route == "Intravenous") %>% 
  # step 1: Flatiron recommendation cleanup
  # 90 days rule between diagnosis and treatment
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  ungroup() %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "days")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "days")) %>% 
  mutate(days_at_first_treatment = case_when(
    therapy == "Upfront Chemo" |
      therapy == "Chemotherapy only"             ~ interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "days"),
    therapy == "Upfront Surgery" |
      therapy == "Surgery Only"                  ~ interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "days")
  )) %>% 
  # 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days")
  ) %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_treatment > 90                 ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup() %>%

  # step 2: Filter patients with clinical characteristics fitting to the study criteria
  # include only patients who received platin and/or taxane
  mutate(had_carbo_pacli = case_when(
    drugname == "paclitaxel" |
      drugname == "carboplatin"             ~ "Yes"
  )) %>% 
  group_by(patientid) %>% 
  fill(had_carbo_pacli, .direction = "updown") %>% 
  ungroup() %>% 
  # include patients with single or dual P/T +/- Bev as frontline treatment
  mutate(line_keep = case_when(# F002B429BE6C6
    (linenumber_adj == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))            ~ NA_character_,
    linenumber_adj == 1                                       ~ "exclude"
  )) %>% 
  group_by(patientid) %>%
  fill(line_keep, .direction = "updown") %>% 
  ungroup() %>%

  # step 3: Filter out patients with missing data
  # remove patients with long gap between surgery and adjuvant start (3 months)
  mutate(interval_surgery_to_adj_start = case_when(
      chemotherapy_type == "Adjuvant" &
        linenumber_adj == 1       
      ~ interval(start = surgerydate, end = linestartdate) / duration(n = 1, units = "months")
    )) %>% 
  mutate(gap_surg_drugs = case_when(
    interval_surgery_to_adj_start > 3                  ~ "exclude"
  )) %>% 
  group_by(patientid) %>% 
  fill(gap_surg_drugs, .direction = "updown") %>% 
  ungroup() %>%

  # step 4: Include patients with treatments following the standard of clinical care
  # exclude patients with more than 1 line as Neo
  mutate(neo_more_more_than_1line = case_when(
    chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1                 ~ "exclude"
  )) %>% 
  group_by(patientid) %>% 
  fill(neo_more_more_than_1line, .direction = "updown") %>% 
  ungroup() %>% 
  # exclude patients with maintenance within their frontline
  mutate(frontline_has_maintenance = case_when(
    linenumber_adj == 1 &
    ismaintenancetherapy == "TRUE"             ~ "exclude"
  )) %>% 
  group_by(patientid) %>% 
  fill(frontline_has_maintenance, .direction = "updown") %>% 
  ungroup() %>% 
  # exclude patients with more than 6 cycles in Neo, more than 9 cycles total 
  # in upfront chemo or more than 9 cycles in upfront surgery
  mutate(too_many_cycle = case_when(
    (linenumber_new == 1 &
       therapy == "Upfront Chemo" &
       total_cycle_increment > 6) |

      (linenumber_new == 2 &
         therapy == "Upfront Chemo" &
         total_cycle_increment > 9) |

>>>>

---
title: "Investigate bsa differences"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

@@

## Investigate bsa differences

@@

```{r loadd}
loadd(drugs)
creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
Frontline <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Frontline.rds")
```

```{r}

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```

```{r combine amount same drug one day}
combined_drugs <- drugs %>% 
  # Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate,
           drugname, units, ismaintenancetherapy) %>%
  summarise_at(vars(route, amount), paste, collapse = ";") %>% # keep them in the data then do sum
  mutate(route = case_when(
    str_detect(route, ";")            ~ "Intravenous", # I checked that all the combined administration are IV
    TRUE                              ~ route
  )) %>% 
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  ungroup() %>% 
  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
  purrr::keep(~!all(is.na(.))) %>%
  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 so remove
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  ))# %>%

@@

```{r line coding}
therapy_line <- combined_drugs %>% 
  # bind again with clinical - was lost while summarizing
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  # Define Adjuvant, Neoadjuvant, chemo or surgery
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = 
           factor(chemotherapy_type, levels = 
                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_neo, had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>%

@@

@@

  # Look at dose dense
  # Code how many time a drug comes up in a cycle
  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
  mutate(dose_dense = n()) %>% 
  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
  ungroup()
```

@@

    therapy == "Upfront Chemo" &
      (
        (chemotherapy_type == "Neoadjuvant" &
           interval_bsa < 31 &
           bsa_date < surgerydate) |
          (chemotherapy_type == "Adjuvant" &
             interval_bsa < 31 &
             # bsa_date < lineenddate &
             bsa_date > surgerydate)
      )                                          ~ interval_bsa,
    TRUE                                         ~ NA_real_
  )) %>%
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425))# %>% # get pretty close results 4269 patients result
  # mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  # select(-bsa_du_bois) %>%

  # Merge with auc
  # left_join(., areaUC, by = c("patientid", "drugname")) %>%
  # mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
  #                         duration(n=1, unit="days"))) %>% 
  # mutate(interval_auc = case_when(
  #   (therapy == "Upfront Surgery" &
  #      interval_auc < 31 &
  #      # auc_date < lineenddate &
  #      auc_date > surgerydate)                  ~ interval_auc,
  #   
  #   therapy == "Upfront Chemo" &
  #     (
  #       (chemotherapy_type == "Neoadjuvant" &
  #          interval_auc < 31 &
  #          auc_date < surgerydate) |
  #         (chemotherapy_type == "Adjuvant" &
  #            interval_auc < 31 &
  #            # auc_date < lineenddate &
  #            auc_date > surgerydate)
  #     )                                          ~ interval_auc,
  #   TRUE                                         ~ NA_real_
  # )) %>%
  # arrange(interval_auc) %>% 
  # distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
  #          cycle_start_date, .keep_all = TRUE) %>% 
  # 
  # # Calculate expected dose
  # mutate(expected_dose = case_when(
  #   drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
  #   drugname == "paclitaxel"                  ~ BSA * target_auc 
  #   # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  # )) %>% 
  # mutate(expected_dose = case_when(
  #   expected_dose > 900 &
  #     target_auc == 6              ~ 900,
  #   expected_dose > 750 &
  #     target_auc == 5              ~ 750,
  #   TRUE                           ~ expected_dose
  # )) %>% 
  # mutate(adjusted_expected_dose = case_when(
  #   drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
  #   drugname == "paclitaxel"                  ~ BSA * target_auc 
  #   # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  # )) %>% 
  # mutate(adjusted_expected_dose = case_when(
  #   adjusted_expected_dose > 900 &
  #     target_auc == 6              ~ 900,
  #   adjusted_expected_dose > 750 &
  #     target_auc == 5              ~ 750,
  #   TRUE                           ~ adjusted_expected_dose
  # )) %>% 
  # group_by(patientid) %>%
  # mutate(first_treatment_date = case_when(
  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
  # )) %>% 
  # ungroup() %>% 
  # mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
  #                  duration(n=1, units = "months")) %>% 
  # arrange(patientid, episodedate)

# Correlation BSA

```{r}
library(ggcorrplot)
Treatment1 <- Treatment1 %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)

# coalesce(bsa_at_dx, bsa_du_bois)
a <- Treatment1 %>% 
  distinct(patientid, cycle_increment, .keep_all = TRUE) %>% 
  select(BSA, bsa_du_bois)
head(a)
# p.mat <- cor_pmat(a)
mat <- cor(a, use = "pairwise.complete.obs")
ggcorrplot(mat, hc.order = TRUE, method = "square",
           insig = "blank", # Leave blank on no significant coefficient
           type = "lower",
           lab = TRUE,
           title = "Correlation",
           show.legend = TRUE, legend.title = "Correlation", show.diag = TRUE,
           lab_col = "darkblue", lab_size = 3,
           sig.level = 0.05, #insig = c("pch", "blank"), pch = 4, pch.col = "black", pch.cex = 10,
           tl.cex = 10,
           tl.srt = 90,
           # digits = 1,
           outline.color = "white",
  ggtheme = ggplot2::theme_gray,
  colors = c("blue", "white", "#E46726")
)

a <-Treatment1 %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(BSA, bsa_du_bois)
head(a)
mat <- cor(a, use = "pairwise.complete.obs")
ggcorrplot(mat, hc.order = TRUE, method = "square",
           insig = "blank", # Leave blank on no significant coefficient
           type = "lower",
           lab = TRUE,
           title = "Correlation",
           show.legend = TRUE, legend.title = "Correlation", show.diag = TRUE,
           lab_col = "darkblue", lab_size = 3,
           sig.level = 0.05, #insig = c("pch", "blank"), pch = 4, pch.col = "black", pch.cex = 10,
           tl.cex = 10,
           tl.srt = 90,
           # digits = 1,
           outline.color = "white",
  ggtheme = ggplot2::theme_gray,
  colors = c("blue", "white", "#E46726")
)
# mat <- matrix(c(1,2,3), nrow = 1, ncol = 3, byrow = TRUE,
#                dimnames = list(c("row1"),
#                                c("C.1", "C.2", "C.3")))
# cor(mat)
```
